How to use the tomography toolkit of SPECFEM3D

### 2015-01-22 doc/GJI_2011_paper_about_the_code/paper_GJI_2011_about_the_code.tex
ran the code beautifier, which now removes accented letters and cleans text and LaTeX files

The next grand challenge involves the development of 3D seismic imaging and inversion tools for the characterization
of earthquakes, Earth `noise', and mapping of Earth's interior on all scales,
that is, to address the seismological inverse problem.
The goal is to harness the power of forward and adjoint modeling tools,
such as \href{http://www.geodynamics.org/cig/software/specfem3d}{SPECFEM3D},
together with modern computers to enhance
the quality of images of Earth’s interior and the earthquake rupture process.
Most traditional tomographic methods utilize traveltime or phase information measured by comparing data with simulations,
and interpret such measurements based on ray theory or other approximate methods.
Because of the limitations of these approximate theories, only parts of seismograms can be used,
and initial models are generally restricted to be spherically symmetric.
With the new generation of modeling tools we can go beyond classical tomography
by using fully 3D initial models \citep[e.g.,][]{Akcelik02,Akcelik03,Askan07a,PChen07b,Fichtner09,Fi11},
and utilizing as much information contained in seismograms as possible \citep[e.g.,][]{Maggi2009,Valentine2010}.
Our approach will be to minimize frequency-dependent phase and amplitude
differences between simulated and observed seismograms based on adjoint techniques in combination with conjugate
gradient methods,
an approach we refer to as `adjoint tomography' \citep{TaLiMaTr09,TaLiMaTr2010}.
The development of such capabilities will affect the fields of exploration geophysics,
regional \& global seismology, ocean acoustics, non-destructive testing, medical tomography and helioseismology.

>>>>

The next grand challenge involves the development of 3D seismic imaging and inversion tools for the characterization
of earthquakes, Earth `noise', and mapping of Earth's interior on all scales,
that is, to address the seismological inverse problem.
The goal is to harness the power of forward and adjoint modeling tools,
such as \href{http://www.geodynamics.org/cig/software/specfem3d}{SPECFEM3D},
together with modern computers to enhance
the quality of images of Earth's interior and the earthquake rupture process.
Most traditional tomographic methods utilize traveltime or phase information measured by comparing data with simulations,
and interpret such measurements based on ray theory or other approximate methods.
Because of the limitations of these approximate theories, only parts of seismograms can be used,
and initial models are generally restricted to be spherically symmetric.
With the new generation of modeling tools we can go beyond classical tomography
by using fully 3D initial models \citep[e.g.,][]{Akcelik02,Akcelik03,Askan07a,PChen07b,Fichtner09,Fi11},
and utilizing as much information contained in seismograms as possible \citep[e.g.,][]{Maggi2009,Valentine2010}.
Our approach will be to minimize frequency-dependent phase and amplitude
differences between simulated and observed seismograms based on adjoint techniques in combination with conjugate
gradient methods,
an approach we refer to as `adjoint tomography' \citep{TaLiMaTr09,TaLiMaTr2010}.
The development of such capabilities will affect the fields of exploration geophysics,
regional \& global seismology, ocean acoustics, non-destructive testing, medical tomography and helioseismology.

### 2015-01-22 utils/ADJOINT_TOMOGRAPHY_TOOLS/ADJOINT_TOMOGRAPHY_TOOLKIT/HowtoUseToolkit.tex
ran the code beautifier, which now removes accented letters and cleans text and LaTeX files

- mention somewhere that Vadim and Sébastien Chevrot will commit their routines to interpolate back and forth between the SEM mesh and a regular mesh; mention that we should talk to Qinya about this, since she was in the process of implementing that as well (I think that Vadim and Sébastien's routine will be sufficient, but we should doublecheck with Qinya if she had something different (more powerful? or faster?) in mind

>>>>

- mention somewhere that Vadim and Sebastien Chevrot will commit their routines to interpolate back and forth between the SEM mesh and a regular mesh; mention that we should talk to Qinya about this, since she was in the process of implementing that as well (I think that Vadim and Sebastien's routine will be sufficient, but we should doublecheck with Qinya if she had something different (more powerful? or faster?) in mind
